---
title: "Hotel Customer Analytic(City Hotel)"
author: "Ray Kwon"
date: "2022-12-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# 1 Introduction

These are two datasets with Portuguese hotel demand data and each observation represents a hotel booking. One of the hotels is a resort hotel(40,060 observations) and other is a city hotel(79,330 observations).

## 1.1 Problem Statement :

What differentiated marketing strategy can attract the exiting customers ?

## 1.2 Goal:

Segmenting all customers using K-mean clustering and then identifying recommendations for hotels by analyzing customer needs.

```{r setrrthup, include=FALSE}
#data minig 

library(dplyr)

hotel <- read.csv("hotel_bookings.csv")

unique(hotel$hotel)

city <- filter(hotel, hotel == "City Hotel")

city$meal_num1 <-  ifelse(city$meal == 'BB',1,ifelse(city$meal == 'FB',2,ifelse(city$meal == "HB",3,ifelse(city$meal=='SC',4,0)))) #labels number on meal

city$depo_num1 <- ifelse(city$deposit_type == "No Deposit", 1, ifelse(city$deposit_type == "Refundable", 2, ifelse(city$deposit_type == "Non Refund", 3, 0)))#labels number on deposit type


city$family1 <- ifelse(city$children > 0 | city$babies > 0, 1,0)


city_demand <- filter(city, adr > 20)


```

# 2 Exploratory Data Analysis (EDA)

There are 5 variables to figure out marketing strategy: Family & Meal Plan & Type of deposit & ADR & Paring space

Family: the customers brought their kids ?

\*Accompanied kids: 1 & NO accompanied kids: 0

Meal Plan: what type of meal plan the customers preferred?

\*No plan: 0 & BB(Breakfast and Bed): 1 & FB(Full Board):2 & HB(Half Board): 3 & SC(Self Catering): 4

Type of Deposit: What type of deposit the customers chose ?

-   No deposit: 1 & Refundable: 2 & Non Refund:3

Parking: How many parking spaces were required by customers?

ADR: Average Daily Rate(Dividing room revenue by rooms sold)

### 2.1 How many kids are accompanied by customers? :

About 90% of customers didn't bring children or babies and few customers brought 1 or 2 children

### 2.2 Types of deposit

About 85% of customers chose 1(No Deposit)

### 2.3 Types of Meal plan

About 75% of customers chose 1(Breakfast and beds) and about 13% of customer chose 4(Self-Catering)

### 2.4 Average Daily Rate

Each room generates \$50 to \$100 per a day mostly

```{r sejhgp}

#install.packages("ggplot2")
library(ggplot2)

ggplot(city_demand, aes(x = children)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1,
                 colour = "goldenrod2", fill = "goldenrod2")+ labs(y= "Number of customers", x = "2.1 Number of accompanied children")+ggtitle("2.1Number of customers who accompanied children")+theme(plot.title = element_text(hjust = 0.5))


ggplot(city_demand, aes(x = babies)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1,
                 colour = "slateblue2", fill = "slateblue3")+ labs(y= "Number of customers", x = "Number of accompanied babies")+ggtitle("2.1 Number of customers who accompanied babies")+theme(plot.title = element_text(hjust = 0.5))


ggplot(city_demand, aes(x = depo_num1)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1,
                 colour = "aquamarine3", fill = "aquamarine3")+ labs(y= "Number of customers", x = "Type of Deposit")+ggtitle("2.2 Type of Deposit by Customers")+theme(plot.title = element_text(hjust = 0.5))

ggplot(city_demand, aes(x = meal_num1)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 1,
                 colour = "azure3", fill = "azure3")+ labs(y= "Number of customers", x = "Type of Meal Plan")+ggtitle("2.3 Type of Meal Plan by Customers")+theme(plot.title = element_text(hjust = 0.5))


ggplot(city_demand, aes(x = adr)) +
  geom_histogram(aes(y = after_stat(count)), binwidth = 5,
                 colour = "antiquewhite2", fill = "antiquewhite2")+ labs(y= "Number of customers", x = "Average Daily Rate")+ggtitle("Average Daily Rate by Customers")+theme(plot.title = element_text(hjust = 0.5))+ stat_bin(bins = 10)

```

# 3 Normalization

### Distance of clusters is highly influenced by scale of variables, it is customary to normalize first. In our dataset, all variables are on not same scale(0,1), so normalization is necessary

```{r sjonniitup}

city_demand <- na.omit(city_demand)

city_cluster <- city_demand[c("family1", "meal_num1", "depo_num1", "adr", "required_car_parking_spaces")]


#install.packages("caret")
library(caret)

preproc1 = preProcess(city_cluster)

cityClusterNorm = predict(preproc1, city_cluster)
```

# 4 Elbow Curve

## 4.1 why we need to use elbow curve ?

We need use elbow curve to figure out what is the optimal number of cluster. The graph looks like elbow shape and we need to find elbow point that is k-value where the elbow gets created. This is because increasing the value of "K" does not reduce WCSS(Within-Cluster Sum of Square)

## 4.2 Optimal number of cluster

We choose the elbow point which is 6. Even though we increasd the k-value, it does not reduce WCSS.

```{r se}
# elbow curve 

dat.sample2 <- cityClusterNorm[sample(nrow(cityClusterNorm), size = 2000, replace = FALSE), ]

dat.sample3 <- na.omit(dat.sample2)




#install.packages("factoextra")
library(cluster)
library(factoextra)

fviz_nbclust(dat.sample3, kmeans, method = "wss")
```

# 5 Result of K-mean Clustering

## 5.1 Size of Clusters

Cluster1: 29,009 Cluster2: 14,885 Cluster3: 12,852 Cluster4: 14,279 Cluster5: 1,873 Cluster6: 4,995

## 5.2 Insight

### °Cluster6 show the highest average daily rate

### °All clusters chose "No deposit" except cluster 3 that chose "Non refund" option

### °Customers in cluster6 brought their kids

### °Most customers in cluster4 chose Half Board or self-catering, whereas, most customers in rest clusters chose "Breakfast and Bed" option

### °Cluster5 required parking space

```{r sesdfp}
set.seed(1234)
cityClusterNorm <- na.omit(cityClusterNorm)

kmeansClustering_city <- kmeans(cityClusterNorm, centers = 6)

table(kmeansClustering_city$cluster)


tapply(city_cluster$family1, kmeansClustering_city$cluster, mean)
tapply(city_cluster$adr, kmeansClustering_city$cluster, mean)
tapply(city_cluster$depo_num1, kmeansClustering_city$cluster, mean)
tapply(city_cluster$meal_num1, kmeansClustering_city$cluster, mean)
tapply(city_cluster$required_car_parking_spaces, kmeansClustering_city$cluster, mean)
```

```{r ftup}

library(RColorBrewer)
library(tidyr)

Num_cluster <- c(1:6)
center1 <- kmeansClustering_city$centers

center_df1 <- data.frame(Num_cluster,center1)

hm.palette <-colorRampPalette(rev(brewer.pal(10, 'RdYlGn')),space='Lab')

center_reshape1 <- gather(center_df1, features, values, family1:required_car_parking_spaces)

heat_map1<- ggplot(data = center_reshape1, aes(x = features, y= Num_cluster, fill = values))+scale_y_continuous(breaks = seq(1, 6, by = 1)) +
    geom_tile() +
    coord_equal() +
    scale_fill_gradientn(colours = hm.palette(90)) +
    theme_classic()

heat_map1+labs(y= "Cluster", x = "Customer Propensity")+ggtitle("Customer Propensity by Cluster")+theme(plot.title = element_text(hjust = 0.5))+scale_x_discrete(labels=c('ADR', 'Deposit', 'Family',"Meal Plan","Parking"))



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
